Classless Java

### 2015-11-09 paper/sections/Formalization.tex

\section{Formal Semantics}\label{sec:formal}
\marco{Old notes: new text is later}
Yanlin and Haoyuan

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=5in]{table.png}
\caption{Table.}\label{table_png}
\end{figure}

>>>>

\section{Formal Semantics}\label{sec:formal}

\subsection{Method Overriding Bug in Java}
\begin{figure}[tbp]
\centering
\includegraphics[width=5in]{table.png}
\caption{Table.}\label{fig:javabug}
\end{figure}

Figure~\ref{fig:javabug} shows the method overriding mechanism in Java. In the
example, there are 6 interfaces \texttt{A1,A2,A3,B1,B2,B3} with methods all
named as \texttt{m} which are either abstract or default methods. If we define a
new interface \texttt{M} that extends two of these interfaces, then the method
overriding result is shown in the table. For example, row2 col2 means \texttt{M
  extends A1,B1}. The result is \texttt{ERROR} because the abstract method
\texttt{T m();} in \texttt{A1} conflicts with the method \texttt{default T m()
  {...}} in \texttt{B1}. Readers may also figure out other extending cases by
following this way of interpretation. The interesting case in row4 col2 where
\texttt{M extends A1,B3}, the result should be \texttt{ERROR}, however in Java
the experimental result is \texttt{B3.m}. Because if we think consistently, this
case is esencially a method conflicting situation with abstract methods and
default methods, which is no different than the first case.

\lstinputlisting[linerange=5-10]{../UseMixinLombok/src/methodshadowing/test5/Test5.java} % APPLY:linerange=JAVABUG

In our approach, we overcome this bug by detecting method correctness when
typechecking all interfaces.

\marco{Old notes: new text is later}
Yanlin and Haoyuan

@@

### 2015-11-09 paper/sections/RelatedWork.tex

\paragraph{ThisType/MyType/Extensibility}
Typical object-oriented programming languages (e.g. Java) use class names as
types and inheritance as subtyping relations. This gives difficulty when
extending classes/interfaces with recursive types. Problems such as binary
methods, return type refinement, etc. emerge and hinders software extensibility
greatly.

@@

\paragraph{Type-Directed Translations/Syntactic Sugar}

- SugarJ~\cite{erdweg11sugarj}

@@

\paragraph{Meta-programming techniques}
- MetaFJig*

>>>>

\subsection{ThisType/MyType/Extensibility}
Typical object-oriented programming languages (e.g. Java) use class names as
types and inheritance as subtyping relations. This gives difficulty when
extending classes/interfaces with recursive types. Problems such as binary
methods, return type refinement, etc. emerge and hinders software extensibility
greatly.

@@

\subsection{Type-Directed Translations/Syntactic Sugar}
Language extensions are often implemented as syntactic sugar of the base
language. For example, Scala compiler supports XML syntax in normal Scala code
directly (after Scala ?, users need to import \texttt{scala-xml} library
manually). However, this approach is hard in terms of implementation, because it
requires extending the compiler. Also, this approach does not support combining
multiple extensions into one.

SugarJ~\cite{erdweg11sugarj} is a Java-based extensible programming language
that allows programmers to extend the base language with custom language
features by definitions in meta-DSLs (SDF, Stratego, etc). 
\yanlin{Is new syntax really a ``drawback''? I think for some system, like
  SugarJ, one of purpose IS to introduce these new syntax.}  Drawbacks: new
syntax. To create the extension, programmers have to work with multiple
languages (SDF, stratego, etc) while our approach works totally in Java
environment.

@@

\paragraph{Meta-programming techniques}
- MetaFJig*
\yanlin{Maybe Marco can help with the text for MetaFJig?}
